\documentclass[]{article}

\begin{document}

\title{Self­‑assesment Professional Attitude}
\author{Perceptum team}
\date{\today}
\maketitle

For {\bf organization}, we award ourselves a 10. During the project we were organized towards our client and academic mentor. Raquel was away during a large part the project, besides some mail contact to set a meeting we only met with her twice. As a team we were complete,  on time and well prepared during these meetings. These meetings were our only `official' meetings during the month. Because we mostly worked across the hall from our client, most of the discussions or progress reports were ad hoc meetings based whenever one of us needed to know something.

For {\bf communication}, we award ourselves a 10. During the project, Perceptum supplied our team with an office. We used this office whenever possible and for the major part of the project our client was across the hall. Because of this we were able to quickly report our progress and decide on next steps together. Our academic supervisor was away for most of the project, we mostly communicated through email. Besides that we have kept  a daily journal with progress and decisions which was available to her and our client.

For {\bf drive and motivation}, we award ourselves a 10. During this project, we spent nearly all our available time on site at Percuptum. Due to personal and other study related limitations, this was not always possible but we believe we have put tremendous effort into this project. Some days we lunched with the Perceptum team and discussed progress and ideas about Starfish. During the first week, we did not only work on the proposed method but also searched existing literature for solutions and new initiatives. Outcomes like the network specific weighting and threshold were then extensively discussed with the client to try to fit them into the project.

Overall we think our attitude was very professional. We have communicated clearly with our supervisor and client and delivered a product which is in line with the expectations that were set and adjusted during the project. We regularly talked with involved parties, met deadlines and have put a great deal of work into this project. We are very happy Perceptum was able to supply us with a workspace which allowed for such close collaboration that we think we have worked on this project to everyone's satisfaction with a very interesting product and analysis.



\end{document}