
% DO NOT COMPILE THIS FILE DIRECTLY!
% This is included by the other .tex files.

\section{Domain}
The starfish current Starfish document graph contains 240 documents which are directionally linked. Each document in this graph is of one of the following types: Information, Glossary, Question, Good Practice, Project, Person or Event. Documents have an author, title, text, tags and links. Some document types have different optional fields like `name' for person and `headline' for good practices and projects. 

Glossaries are special types of documents, as they are description for tags. Because different groups use alternative names to describe concepts, tags may be aliases. Of the 210 tags the current system contains, x unique tag concepts can be distinguished of which x\% has a glossary. On average a document has x tags, x outgoing links, and x incoming links.

These numbers and properties of the system give some insight into the current state of the dataset and possible solutions. Due to the nature of the directional links, semantical document analysis will probably not be enough to correctly propose links. A novel Starfish specific method could be combined with this well known symmetrical measure for optimal results. Starfish mostly contains documents in English, but a small part of the data is in Dutch. This language diversity and the fact that documents can also be non-textual like images or videos indicate a system that is not purely based on text will perform better.